MLH1 Data Report

### 2019-06-11 doc/Main_Report.rmd
starting writing up the main results report

---
title: 'MLH1 Data Report'
author: "April Peterson"
date: "29 may 2018"
output: rmarkdown::github_document
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

```{r,echo=FALSE}
#set the order of another column, based on another variable (so that when)

@@

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
              "WSB", "PWD","MSM","KAZ","CAST","HMI","SPRET","SPIC", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=TRUE}
### to integrate 'pass'/fail
### this should be in setup data

#quant_status (this isn't saving)
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
}

#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,16,22) ]

@@

#df list, is a list of df's which were split() from BIG df by category
df_list 
o=0
i=0

MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ geom_jitter(aes(y= adj_nMLH1.foci, x= quality))
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)
#  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL)

# +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))

  plot_list[[h]] =   pf
}

#orig
plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf +geom_rect(data = df_list[[h]], aes(fill=quant_status), xmin=-100, xmax=100, ymin=-100, ymax=100, alpha=0.005)

    pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +

    scale_fill_manual(values=alpha(c("red"), .005), breaks=NULL)

    #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
  plot_list[[h]] =   pf
}
#can't change the alpha/transparency of the red rec

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')

for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```

@@

```{r, include=FALSE}
passed_mice_data <- MLH1_data[MLH1_data$mouse %in% passed_mice, ]
non_passed_mice_data <- MLH1_data[MLH1_data$mouse %in% not_passed, ]

#make a column to mark if observation comes from passed or not passed mouse
#turn this into boxplot and sort the category order, otherwise it's hard to any patterns
sc <- qplot(mouse, nMLH1.foci,  colour = category, data = non_passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

sc <- qplot(mouse, nMLH1.foci,  colour = category, data = passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

>>>>

---
title: "MLH1 Data Report"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="data/MLH1/MLH1_data_setup.RData")
```

@@

```{r organizing.data, echo=FALSE}
#set the order of another column, based on another variable (so that when)

@@

```{r missing.mice, echo=FALSE}

setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
setwd("~./MLH1repo/")
#other lists

Image_dirs <- list.files(path = "C:/Users/alpeterson7/Documents/Images")
#write this out so that I can access it

#remove the non-mouse folders
Dissection.File = read.csv("~./MLH1repo/data/Disections_53019.csv", header = TRUE)
Dissection.File <- Dissection.File[!(is.na(Dissection.File$mouse)|Dissection.File$mouse==""),]

#print the name with the date of the file somewhere
Dissection.list <- Dissection.File$mouse
Dissection.list <- as.character(Dissection.list)

#load metadata .. start decerning which mice are missing information... and which should be used
Meta.Data.File = read.csv("~./MLH1repo/data/ALP_MouseMetadata.csv", header = TRUE)

#remove file name, and original name .. this is just a mouse level DF
Meta.Data.File <- Meta.Data.File[!(is.na(Meta.Data.File$mouse)|Meta.Data.File$mouse==""),]
#make sure that the DOB is a date

meta.data.file2 = read.csv("~./MLH1repo/data/MouseMetaData61019.csv", header = TRUE)
meta.data.file2$DOB <- as.Date(meta.data.file2$DOB, format= "%m/%d/%y")

jl <- unique(Meta.Data.File$mouse[(Meta.Data.File$mouse %in% Dissection.File$mouse)])
BD.w.meta <- Meta.Data.File[(Meta.Data.File$mouse %in% Dissection.File$mouse), ]

#figure out a way to incorporate the staining... to get a better idea of which slides 
#to do next, #remove the pero mice?

#length(unique(MLH1_data$mouse) )

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
original_DF$fileName <- (original_DF$Original.Name)
original_DF <- add_mouse(original_DF)
#length(unique(original_DF$mouse) )
#131 mice have been quant total, 124 mice have passed into the final version

# make a list for the failed slides

#Dissection.list - Image/dirs
NonImaged.mice <- unique(Dissection.File$mouse[(Dissection.File$mouse %in% Image_dirs)])
#231 mice dissected which need images

#ImageFolder - MLH1.Quant
NonQuant.mice <- unique(Image_dirs[(Image_dirs %in% MLH1_data$mouse )])
#length(NonQuant.mice)
#123 mice that need to get into anon-batch

#make Dataframe to put into a table
mouse.number.DF <- data.frame( category = 
              c("Passed Quantified", "Total Quantified", "Non-Quantified", "Non-Imaged"),
              number.of.mice = c(length(unique(MLH1_data$mouse)),
                length(unique(original_DF$mouse) ),
                        length(NonQuant.mice),
                         length(NonImaged.mice)  )  )

kable(mouse.number.DF)
```

This is the number of mice that are through different parts of the pathway or quantification process.

```{r basic.numbers, echo=FALSE}

kable(table(AP_mouse_table$category), col.names = c("Category", "mice"), label = "Number of mice by category" )

kable(table(MLH1_data$category), col.names = c("Category","Cells"), label = "Number of Cells by category" )

These are the tables for the number of mice and cells which have been quantified. (what is in the 'other' category?)

@@

```{r first.boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
              "WSB", "PWD","MSM","KAZ","CAST","HMI","SPRET","SPIC", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.

```{r, echo=FALSE, message=FALSE, results='hide', warning=TRUE}
### to integrate 'pass'/fail
### this should be in setup data

#quant_status (this isn't saving)
#for(i in 1:length(MLH1_data$mouse)){
#  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
#}

#what is the purpose of this block
#df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#df_list <- df_list[ -c(7,16,22) ]

@@

#df list, is a list of df's which were split() from BIG df by category
#df_list 
#o=0
#i=0

#MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
#for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
#  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
#  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
 #                      mouse_nMLH1 = mean(adj_nMLH1.foci)
#  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
#  for(o in 1:length(df_list[[i]]$Original.Name)){
#    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == #sub_mouse_means$mouse) ]
#        }
#}

#plot_list = list()
#for (h in 1:length(df_list)) {
#  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ #geom_jitter(aes(y= adj_nMLH1.foci, x= quality))
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)
#  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL)

# +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
#  
#  plot_list[[h]] =   pf
#}

#orig
#plot_list = list()
#for (h in 1:length(df_list)) {
#  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
#  pf <- pf +geom_rect(data = df_list[[h]], aes(fill=quant_status), xmin=-100, xmax=100, #ymin=-100, ymax=100, alpha=0.005)

#    pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
#  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
#  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") #+

#    scale_fill_manual(values=alpha(c("red"), .005), breaks=NULL)

    #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
#  plot_list[[h]] =   pf
#}
#can't change the alpha/transparency of the red rec

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
#geom_hline(aes(yintercept = med, group = gr), colour = 'red')
#
#for (gg in 1:length(plot_list) ){
#  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
#}
```

@@

```{r, include=FALSE}
#passed_mice_data <- MLH1_data[MLH1_data$mouse %in% passed_mice, ]
#non_passed_mice_data <- MLH1_data[MLH1_data$mouse %in% not_passed, ]

#make a column to mark if observation comes from passed or not passed mouse
#turn this into boxplot and sort the category order, otherwise it's hard to any patterns
#sc <- qplot(mouse, nMLH1.foci,  colour = category, data = non_passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

#sc <- qplot(mouse, nMLH1.foci,  colour = category, data = passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")
